Ancestry linkage in hybrid zones

### 2016-02-06 drafts/hybrid_zone.tex
added yanivs words

Numerical solution for the PDE can be used on real, non-flat landscapes that change with time;
we have code and notes on solving them on github.

>>>>

%% yaniv says:
\paragraph{Signals of block length}
\plr{or, perhaps for introduction?}
In addition to our finding that ancestry surrounding selected sites was quite long, our simulations revealed a consistent and unexpected finding. We found, on a given side of the hybrid zone, a transition from the locally adaptive ancestry at the selected site to the alternative ancestry at a closely linked site was short-lived. Put differently, blocks of 'wrong' ancestry that do not overlap the selected site but are closely linked are exceptionally short.

A simple intuitive explanation for this pattern suggests itself - loci physically linked to the selected sites can only survive on the wrong side of the hybrid zone for a reasonable amount of time if they recombine away from their ancestry at the locally adaptive site. Because it is then tightly linked to the alternate ancestry at the selected site, this ancestry chunk will large recombine with the alternate ancestry, and therefore decay rapidly.

\paragraph{Solutions to PDE}
Numerical solution for the PDE can be used on real, non-flat landscapes that change with time;
we have code and notes on solving them on github.
